---
title: "Capstone Project"
author: "Swati Jani Joshi"
date: "November 18 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Springboard Capstone Project

This is the Springboard Capstone Prject Code. The data set is from kaggle Prima Indians Diabetes Database found <https://www.kaggle.com/uciml/pima-indians-diabetes-database>

#### Read and Load Data
```{r cars}
library("ROCR")
library(ggplot2)
diabetes <- read.csv("~/Documents/Springboard Capstone Project/Data Files/diabetes.csv")
```

#### Examine the Structure of the Dataset
```{r}
str(diabetes)
```

#### Data Manipulation
##### Since it is not possible for a person to have Blood Pressure, Skin Thickness and Insulin of 0 those observations will be removed 
```{r}
diabetes$Outcome <- factor(diabetes$Outcome)
for (i in 2:6) {
diabetes <- diabetes[-which(diabetes[,i] ==0), ]}
```

#### Examine the Structure of the Modified Dataset
```{r}
str(diabetes)
```

#### Plotting Histograms to better understand the type of distribution
```{r}
hist(diabetes$Pregnancies)
hist(diabetes$Glucose)
hist(diabetes$BloodPressure)
hist(diabetes$SkinThickness)
hist(diabetes$Insulin)
hist(diabetes$BMI)
hist(diabetes$DiabetesPedigreeFunction)
hist(diabetes$Age)
```

#### Splitting the Dataset
```{r}
set.seed(140)
training_set <- sort(sample(nrow(diabetes), nrow(diabetes)*.7))
diabetes_train <- diabetes[training_set,]
diabetes_test <- diabetes[-training_set,]
```

#### Logistic Regression Model
```{r}
model <- glm(Outcome~.,data=diabetes_train,family = binomial(link='logit'))
summary(model)
```

#### Using the model on the Test Set
```{r}
predictions <- predict(model,newdata=diabetes_test,type="response")
predictions <- round(predictions)
mean(predictions==diabetes_test$Outcome)
```

#### Better Logistic Regression Model
```{r}
model2 <- glm(Outcome~Glucose + BMI + DiabetesPedigreeFunction,data=diabetes_train,family = binomial(link='logit'))
summary(model2)
```

#### Using the model on the Test Set
```{r}
predictions2 <- predict(model2,newdata=diabetes_test,type="response")
predictions2 <- round(predictions2)
mean(predictions2==diabetes_test$Outcome)
```

#### ROC Curve
```{r}
p = predict(model2, diabetes_test, type="response")
pr = prediction(p, diabetes_test$Outcome)
prf = performance(pr, measure = "tpr", x.measure = "fpr")
plot(prf)
```

#### AUC
```{r}
auc = performance(pr, measure = "auc")
auc = auc@y.values[[1]]
print(paste("Model Accuracy", auc))
```